\chapter{Introduction}
\label{chap:introduction}
The twentieth century brought us two major cornerstones in physics: quantum mechanics and general relativity. Whilst quantum mechanics successfully describes physics at the smallest scales and general relativity describes physics at the largest scales, a unified theory of quantum gravity is still missing. To test whether gravity is a quantum entity (the existence of gravitons) an experiment was proposed by \textcite{bose_spin_2017}.

The experiment proposed by \citeauthor{bose_spin_2017} suggests entangling two particles through gravity. If this is possible, it would be a direct proof that gravity is a quantum entity. To realize this experiment, we need two small ($\approx \qty{1}{\micro\meter}$) but massive particles isolated from their environment and cooled to their ground state. An electronic spin is attached to the particles and a $\pi/2$-pulse is applied to the spins. This creates a superposition of spins. The particles are then dropped through a Stern-Gerlach interferometer which turns the superposition of spins into a superposition of positions. The two particles are then allowed to interact through gravity. This interaction entangles the particles. The outcome of the experiment is measured by the interference of the particles.

In this thesis we focus on the levitation of micrometer sized particles using a planar magnetic Paul trap. A magnetic Paul trap uses an ac magnetic field to obtain stable levitation. This builds on previous work within our group where a \qty{250}{\micro\meter} cubic \ce{NdFeB} magnet was levitated in a planar magnetic Paul trap realized on a PCB\cite{eli, mart}. In order to work towards the quantum regime, the system needs to be miniaturized.

Two other well known levitation techniques are optical (eigenfrequencies between \qtyrange{10}{300}{\kilo\hertz}) and electrical traps (eigenfrequencies between \qtyrange{1}{10}{\kilo\hertz})\cite{levitodynamics}. Compared to these techniques, magnetic traps have the disadvantage of having a lower eigenfrequency (\qtyrange{1}{10}{\kilo\hertz}), often require cryogenic temperatures and no on-chip integration exists\cite{levitodynamics}. The advantage however is that magnetic traps have the potential to levitate much larger and heavier particles. Levitating heavier particles creates a strong gravitational interaction which is beneficial for the experiment.

The cryogenic necessity originates from the fact that many magnetic traps use the Meissner effect to levitate a particle. An alternative to this however is to use non-static magnetic fields which then also satisfies Earnshaw's theorem. Previous work has shown this to be possible\cite{perdriat,eli,mart}. The goal of this project is to create an on-chip variant of the magnetic Paul trap. Besides the advantage of an on-chip design, this will also increase the eigenfrequency of the trap\cite{perdriat}.
